Prefix-free graphs and suffix array construction in sublinear space

### 2023-06-24 manuscript/comparison_table.tex
finished iterator preparation
finished?

\begin{table*}
    \label{tab:segment}
    \begin{tabular}{rllll}
        \toprule
        \#sequences & pggb & vg & minigraph-cactus & PFG \\
        \midrule
        % 2 &
        4   & 0m12s & 0m1s  & 3m47s  & 0m1s \\
        16  & 0m19s & 0m1s  & 6m30s  & 0m1s \\
        64  & 1m20s & 0m2s  & 13m30s & 0m1s \\
        256 & 7m20s & 0m55s & 41m49s & 0m3s \\
        \bottomrule
    \end{tabular}
    \caption{
        Comparison of running times of pangenomic graph construction tools.
        Some of these tools need some kind of preprocessing in order to build the graph.
        pggb requires for the fasta files to be indexed.
        In our case, due to the small size of our files, this time was negligible, but it can have a bigger impact when bigger genomes are considered.
        VG builds a pangenome graph starting from a VCF file or a multiple sequence alignment.
        In each case, those outputs require to perform time consuming steps.
        Having a suitable VCF file requires to align each haplotype to a reference genome and subsequently performing variant calling.
        Beyond being time consuming, using a linear reference in a first place can introduce some biases in the first place.
        On the other hand, performing a multiple sequence alignment is also known to be potentially slow, according to the length and the abundance of the underlying sequences.
    }
\end{table*}

>>>>

\begin{table*}
    \label{tab:comparison}
    \begin{tabular}{rrrrr}
        \toprule
        \#seqs & pggb & vg & minigraph-cactus & pfg \\
        \midrule
        4   & 0m 12s & 0m 1s  & 3m 47s  & 0m 1s \\
        16  & 0m 19s & 0m 1s  & 6m 30s  & 0m 1s \\
        64  & 1m 20s & 0m 2s  & 13m 30s & 0m 1s \\
        256 & 7m 20s & 0m 55s & 41m 49s & 0m 3s \\
        \bottomrule
    \end{tabular}
    \caption{
        Comparison of running times of pangenomic graph construction tools.
        Wall clock times are measured by the built-in bash command \texttt{time} and rounded up to the nearest second.
        In addition to the measured times, \texttt{pggb} and \texttt{vg} need preprocessing of the pangenome.
        \texttt{pggb} requires the fasta file to be indexed.
        This time was negligible in our case, but it can have a more significant impact when a more extensive dataset is considered.
        \texttt{vg} builds a pangenome from a VCF file or a multiple sequence alignment.
        In both cases, acquiring this data requires time-consuming steps.
        Furthermore, variant calling using a linear reference can introduce a reference bias.
    }
\end{table*}
